Provably Correct, Low-Cost Optimizations for Abstract Abstract Machines

### 2013-03-20 paper/paper.tex
Small change to conclusion.

Correctness here requires a lemma that relates the differences in the compilation functions.
\begin{lemma}[Compile coherence]
For all $\mexp, \mcntr,\menv,\msto,\msdiff,\mkont,\msto^*,\mkont^*$,
if $\msto \equiv \msto^*$ and $\mkont \equiv \mkont^*$, then
$\dcompile{\mexp}^\mcntr(\menv,\msto,\msdiff,\mkont) = \ttuple{\mastate}{\msdiff'}$ iff
$\compile{\mexp}^\mcntr(\menv,\msto^*,\mkont^*) = \mstate$ such that
$\mastate,\replay(\msdiff',\msto) \equiv \nw(\mstate)$
\end{lemma}
Proof is by induction on $\mexp$.

@@

Abstract machines are not only a good model for rapid analysis
development, they can be systematically developed into efficient
algorithms.

>>>>

Correctness here requires a lemma that relates the differences in the compilation functions.
\begin{lemma}[Compile coherence]
If $\msto \equiv \msto^*$ and $\mkont \equiv \mkont^*$, then
$\dcompile{\mexp}^\mcntr(\menv,\msto,\msdiff,\mkont) = \ttuple{\mastate}{\msdiff'}$ iff
$\compile{\mexp}^\mcntr(\menv,\msto^*,\mkont^*) = \mstate$ such that
$\mastate,\replay(\msdiff',\msto) \equiv \nw(\mstate)$
\end{lemma}
Proof is by induction on $\mexp$.

@@

Abstract machines are not only a good model for rapid analysis
development, they can be systematically developed into efficient
algorithms that can be proved correct.
